19Q2

### 2020-01-14 19Q2.Rmd

g2p_dgl <-  as.character(unique(g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)]))
g2p_dg <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
g2p_drugs <- as.character(unique(g2p$Drug[!is.na(g2p$Drug)]))
g2p_genes <- as.character(unique(g2p$Gene[!is.na(g2p$Gene)]))
g2p_dg_genes <- unique(sapply(strsplit(g2p_dgl, "_", fixed = TRUE), function(x) x[2]))
g2p_lins <- as.character(unique(g2p$group_general_lineage_name[!is.na(g2p$group_general_lineage_name)]))

@@

  if(metric == "GE") {
    if(lineage) {
      df_count <- df %>% drop_na(TPM) %>% count(Drug, Gene, disease, Drug_Gene_Lin)
      df_count_filt <- filter(df_count, n >= 3)
      df_filt <- filter(df, Drug_Gene_Lin %in% df_count_filt$Drug_Gene_Lin)
      res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, 
                  GE_p_log10 = -log10(GE_p))
      res$Gene_Lin <- with(res, paste0(Gene, "_", disease))
      if(dataset != "CRISPR") { res$InG2P <- ifelse(res$Drug_Gene_Lin %in% g2p_list, "Yes", "No") }
      if(dataset == "CRISPR") { res$InG2P <- ifelse(res$Gene_Lin %in% g2p_list, "Yes", "No") }
      res <- merge(res, df_count, by = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), all = TRUE)
    }
    if(!lineage) {
      df_count <- df %>% drop_na(TPM) %>% count(Drug, Gene, Drug_Gene)
      res <- df %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, 
                  GE_p_log10 = -log10(GE_p))
      if(dataset != "CRISPR") { res$InG2P <- ifelse(res$Drug_Gene %in% g2p_list, "Yes", "No") }
      if(dataset == "CRISPR") { res$InG2P <- ifelse(res$Gene %in% g2p_list, "Yes", "No") }
      res <- merge(res, df_count, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE)
    }
  }
  if(metric == "CN") {
    if(lineage) {
      df_count <- df %>% drop_na(CN) %>% count(Drug, Gene, disease, Drug_Gene_Lin)
      df_count_filt <- filter(df_count, n >= 3)
      df_filt <- filter(df, Drug_Gene_Lin %in% df_count_filt$Drug_Gene_Lin)
      res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value,
                  CN_p_log10 = -log10(CN_p))
      res$Gene_Lin <- with(res, paste0(Gene, "_", disease))
      if(dataset != "CRISPR") { res$InG2P <- ifelse(res$Drug_Gene_Lin %in% g2p_list, "Yes", "No") }
      if(dataset == "CRISPR") { res$InG2P <- ifelse(res$Gene_Lin %in% g2p_list, "Yes", "No") }
      res <- merge(res, df_count, by = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), all = TRUE)
    }
    if(!lineage) {
      df_count <- df %>% drop_na(CN) %>% count(Drug, Gene, Drug_Gene)
      res <- df %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, 
                  CN_p_log10 = -log10(CN_p))
      if(dataset != "CRISPR") { res$InG2P <- ifelse(res$Drug_Gene %in% g2p_list, "Yes", "No") }
      if(dataset == "CRISPR") { res$InG2P <- ifelse(res$Gene %in% g2p_list, "Yes", "No") }
      res <- merge(res, df_count, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE)
    }
  }
  res$Metric <- metric
  res$Dataset <- dataset
  return(res)
}
```

@@

  ht <- Heatmap(corr_grid,
                col = col_fun,
                na_col = "gray97",
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_heatmap_legend = as.logical(heatmap_legend),
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   location = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                row_title = "Genes",
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "top",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  grid.text(signif_grid[i, j], x = x + width*0.20, y = y + height*0.025, gp = gpar(fontsize = 18))
                  if(annot_grid[i, j] == "sensitivity") {
                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                  }
                  if(annot_grid[i, j] == "resistance") {
                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                  }
                  if(annot_grid[i, j] == "both") {
                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                  }
                }
                )
  return(ht)
}
```

@@

```{r mut_ks_tests}
mut_genes <- union(union(filter(ccle_signif_g2p_dg, InG2P == "Yes")$Gene, filter(ctrp_signif_g2p_dg, InG2P == "Yes")$Gene), filter(gdsc_signif_g2p_dg, InG2P == "Yes")$Gene)
mut_drugs <- union(union(filter(ccle_signif_g2p_dg, InG2P == "Yes")$Drug, filter(ctrp_signif_g2p_dg, InG2P == "Yes")$Drug), filter(gdsc_signif_g2p_dg, InG2P == "Yes")$Drug)

ccle_mut_ht_dat <- filter(ccle_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes)
ks.test(filter(ccle_mut_ht_dat, InG2P == "Yes")$p, filter(ccle_mut_ht_dat, InG2P == "No")$p)

ctrp_mut_ht_dat <- filter(ctrp_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes)
ks.test(filter(ctrp_mut_ht_dat, InG2P == "Yes")$p, filter(ctrp_mut_ht_dat, InG2P == "No")$p)

gdsc_mut_ht_dat <- filter(gdsc_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes)
ks.test(filter(gdsc_mut_ht_dat, InG2P == "Yes")$p, filter(gdsc_mut_ht_dat, InG2P == "No")$p)
```

@@

```{r prot_ks_tests}
ccle_prot$disease_g2p <- ifelse(ccle_prot$disease %in% g2p_diseases, ccle_prot$disease, "other")
ctrp_prot$disease_g2p <- ifelse(ctrp_prot$disease %in% g2p_diseases, ctrp_prot$disease, "other")
gdsc_prot$disease_g2p <- ifelse(gdsc_prot$disease %in% g2p_diseases, gdsc_prot$disease, "other")

ccle_signif_prot_summ <- filter(ccle_signif_prot, InG2P == "Yes") 
ctrp_signif_prot_summ <- filter(ctrp_signif_prot, InG2P == "Yes") 
gdsc_signif_prot_summ <- filter(gdsc_signif_prot, InG2P == "Yes")

prot_drugs <- union(union(ccle_signif_prot_summ$Drug, ctrp_signif_prot_summ$Drug), gdsc_signif_prot_summ$Drug)
prot_drugs <- prot_drugs[!(prot_drugs %in% c("cabozantinib", "vandetinib"))]

ccle_prot_ht_data <- filter(ccle_signif_prot_4plot, Drug %in% prot_drugs)
ks.test(filter(ccle_prot_ht_data, InG2P == "Yes")$p, filter(ccle_prot_ht_data, InG2P == "No")$p)

ctrp_prot_ht_data <- filter(ctrp_signif_prot_4plot, Drug %in% prot_drugs)
ks.test(filter(ctrp_prot_ht_data, InG2P == "Yes")$p, filter(ctrp_prot_ht_data, InG2P == "No")$p)

gdsc_prot_ht_data <- filter(gdsc_signif_prot_4plot, Drug %in% prot_drugs)
ks.test(filter(gdsc_prot_ht_data, InG2P == "Yes")$p, filter(gdsc_prot_ht_data, InG2P == "No")$p)
```

@@

```{r cn_ge_ks_tests}
cn_genes <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
cn_drugs <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)

ccle_cn_ht_data <- filter(cn_cor, Dataset == "CCLE" & Drug %in% cn_drugs & Gene %in% cn_genes)
ks.test(filter(ccle_cn_ht_data, InG2P == "Yes")$CN_p, filter(ccle_cn_ht_data, InG2P == "No")$CN_p)
ctrp_cn_ht_data <- filter(cn_cor, Dataset == "CTRP" & Drug %in% cn_drugs & Gene %in% cn_genes)
ks.test(filter(ctrp_cn_ht_data, InG2P == "Yes")$CN_p, filter(ctrp_cn_ht_data, InG2P == "No")$CN_p)
gdsc_cn_ht_data <- filter(cn_cor, Dataset == "GDSC" & Drug %in% cn_drugs & Gene %in% cn_genes)
ks.test(filter(gdsc_cn_ht_data, InG2P == "Yes")$CN_p, filter(gdsc_cn_ht_data, InG2P == "No")$CN_p)

ge_genes <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
ge_drugs <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)

ccle_ge_ht_data <- filter(ge_cor, Dataset == "CCLE" & Drug %in% ge_drugs & Gene %in% ge_genes)
ks.test(filter(ccle_ge_ht_data, InG2P == "Yes")$GE_p, filter(ccle_ge_ht_data, InG2P == "No")$GE_p)
ctrp_ge_ht_data <- filter(ge_cor, Dataset == "CTRP" & Drug %in% ge_drugs & Gene %in% ge_genes)
ks.test(filter(ctrp_ge_ht_data, InG2P == "Yes")$GE_p, filter(ctrp_ge_ht_data, InG2P == "No")$GE_p)
gdsc_ge_ht_data <- filter(ge_cor, Dataset == "GDSC" & Drug %in% ge_drugs & Gene %in% ge_genes)
ks.test(filter(gdsc_ge_ht_data, InG2P == "Yes")$GE_p, filter(gdsc_ge_ht_data, InG2P == "No")$GE_p)
```

@@

```{r lineages_ks_tests, warning=FALSE}
ks.test(filter(ccle_signif_dgl, InG2P == "Yes")$p, filter(ccle_signif_dgl, InG2P == "No")$p)$p.value
ks.test(filter(ctrp_signif_dgl, InG2P == "Yes")$p, filter(ctrp_signif_dgl, InG2P == "No")$p)$p.value
ks.test(filter(gdsc_signif_dgl, InG2P == "Yes")$p, filter(gdsc_signif_dgl, InG2P == "No")$p)$p.value

ks.test(filter(ccle_signif_prot_lin, InG2P == "Yes")$p, filter(ccle_signif_prot_lin, InG2P == "No")$p)$p.value
ks.test(filter(ctrp_signif_prot_lin, InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, InG2P == "No")$p)$p.value
ks.test(filter(gdsc_signif_prot_lin, InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, InG2P == "No")$p)$p.value

ks.test(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "No")$CN_p)$p.value
ks.test(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "No")$CN_p)$p.value
ks.test(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "No")$CN_p)$p.value

ks.test(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "No")$GE_p)$p.value
ks.test(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "No")$GE_p)$p.value
ks.test(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "No")$GE_p)$p.value

@@

png(filename = "./plots/manuscript_final/drug_lin__pancancer.png", width = 18, height = 8, units = "in", res = 500)
grid.arrange(layout_matrix = lay, grobs = gs_cn_ge)
dev.off()
```

>>>>

g2p_dgl <-  as.character(unique(g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)]))
g2p_dg <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
g2p_drugs <- as.character(unique(g2p$Drug[!is.na(g2p$Drug)]))
g2p_genes <- as.character(unique(g2p$Gene[!is.na(g2p$Gene)]))
g2p_dg_genes <- unique(sapply(strsplit(g2p_dgl, "_", fixed = TRUE), function(x) x[2]))
g2p_lins <- as.character(unique(g2p$disease[!is.na(g2p$disease)]))

@@

  if(metric == "GE") {
    if(lineage) {
      df_count <- df %>% drop_na(TPM) %>% count(Drug, Gene, disease, Drug_Gene_Lin)
      df_count_filt <- filter(df_count, n >= 3)
      df_filt <- filter(df, Drug_Gene_Lin %in% df_count_filt$Drug_Gene_Lin)
      res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
        summarize(GE_r = cor.test(y = Score, x = TPM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
                  GE_p = cor.test(y = Score, x = TPM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, 
                  GE_p_log10 = -log10(GE_p))
      res$Gene_Lin <- with(res, paste0(Gene, "_", disease))
      if(dataset != "CRISPR") { res$InG2P <- ifelse(res$Drug_Gene_Lin %in% g2p_list, "Yes", "No") }
      if(dataset == "CRISPR") { res$InG2P <- ifelse(res$Gene_Lin %in% g2p_list, "Yes", "No") }
      res <- merge(res, df_count, by = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), all = TRUE)
    }
    if(!lineage) {
      df_count <- df %>% drop_na(TPM) %>% count(Drug, Gene, Drug_Gene)
      res <- df %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
        summarize(GE_r = cor.test(y = Score, x = TPM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
                  GE_p = cor.test(y = Score, x = TPM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, 
                  GE_p_log10 = -log10(GE_p))
      if(dataset != "CRISPR") { res$InG2P <- ifelse(res$Drug_Gene %in% g2p_list, "Yes", "No") }
      if(dataset == "CRISPR") { res$InG2P <- ifelse(res$Gene %in% g2p_list, "Yes", "No") }
      res <- merge(res, df_count, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE)
    }
  }
  if(metric == "CN") {
    if(lineage) {
      df_count <- df %>% drop_na(CN) %>% count(Drug, Gene, disease, Drug_Gene_Lin)
      df_count_filt <- filter(df_count, n >= 3)
      df_filt <- filter(df, Drug_Gene_Lin %in% df_count_filt$Drug_Gene_Lin)
      res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
        summarize(CN_r = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
                  CN_p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value,
                  CN_p_log10 = -log10(CN_p))
      res$Gene_Lin <- with(res, paste0(Gene, "_", disease))
      if(dataset != "CRISPR") { res$InG2P <- ifelse(res$Drug_Gene_Lin %in% g2p_list, "Yes", "No") }
      if(dataset == "CRISPR") { res$InG2P <- ifelse(res$Gene_Lin %in% g2p_list, "Yes", "No") }
      res <- merge(res, df_count, by = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), all = TRUE)
    }
    if(!lineage) {
      df_count <- df %>% drop_na(CN) %>% count(Drug, Gene, Drug_Gene)
      res <- df %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
        summarize(CN_r = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
                  CN_p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, 
                  CN_p_log10 = -log10(CN_p))
      if(dataset != "CRISPR") { res$InG2P <- ifelse(res$Drug_Gene %in% g2p_list, "Yes", "No") }
      if(dataset == "CRISPR") { res$InG2P <- ifelse(res$Gene %in% g2p_list, "Yes", "No") }
      res <- merge(res, df_count, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE)
    }
  }
  res$Metric <- metric
  res$Dataset <- dataset
  return(res)
}
```

@@

  ht <- Heatmap(corr_grid,
                col = col_fun,
                na_col = "gray97",
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_heatmap_legend = as.logical(heatmap_legend),
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                column_names_max_height = unit(2, "in"),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   location = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                row_title = "Genes",
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "top",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  grid.text(signif_grid[i, j], x = x + width*0.20, y = y + height*0.025, gp = gpar(fontsize = 18))
                  if(annot_grid[i, j] == "sensitivity") {
                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                  }
                  if(annot_grid[i, j] == "resistance") {
                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                  }
                  if(annot_grid[i, j] == "both") {
                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                  }
                }
                )
  return(ht)
}
```

@@

@@

@@

@@

@@

png(filename = "./plots/manuscript_final/drug_lin_pancancer.png", width = 18, height = 8, units = "in", res = 500)
grid.arrange(layout_matrix = lay, grobs = gs_cn_ge)
dev.off()
```

# SCCB

```{r}
ccle_prot_lin <- filter(ccle_signif_prot_lin, InG2P == "Yes")
ctrp_prot_lin <- filter(ctrp_signif_prot_lin, InG2P == "Yes")
gdsc_prot_lin <- filter(gdsc_signif_prot_lin, InG2P == "Yes")
```

```{r histology_dists_data, eval=FALSE}
hist_count <- function(df, dataset) {
  hists <- unique(select(df, DepMap_ID, disease_g2p)) %>% count(disease_g2p)
  hists$Percent <- hists$n / sum(hists$n) * 100
  hists$Dataset <- dataset
  hists <- hists[order(hists$n, decreasing = T),]
  return(hists)
}

ccle_hists <- hist_count(ccle, "CCLE")
ctrp_hists <- hist_count(ctrp, "CTRP")
gdsc_hists <- hist_count(gdsc, "GDSC")

drug_hists <- rbind(ccle_hists, ctrp_hists, gdsc_hists) %>% drop_na(disease_g2p)
drug_hists$Dataset <- factor(drug_hists$Dataset, levels = c("CCLE", "CTRP", "GDSC"))

png(filename = "./plots/manuscript/all_histology_distributions.png", width = 6, height = 4.5, units = "in", res = 500)
ggplot(drug_hists, aes(x = Dataset, y = n, fill = disease_g2p)) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_manual(values = g2p_disease_colors) +
  scale_y_continuous(breaks = seq(0, 900, by = 100), labels = seq(0, 900, by = 100)) +
  guides(fill = guide_legend(title = "Lineage", ncol = 1)) +
  labs(y = "Count") +
  theme(axis.title.x = element_blank())
dev.off()
```

```{r}
length(unique(g2p_mut$Drug_Gene))
length(unique(g2p_mut$Drug_Gene_Lin))
length(unique(g2p_amp$Drug_Gene_Lin))

g2p_mut_egfr <- filter(g2p_mut, Gene == "EGFR") %>% select(Drug_Gene_Lin, Protein_Change, Direction_Curated)

test2 <- filter(cn_cor_lin, Drug != "CRISPR" & InG2P == "Yes")
test <- filter(ge_cor_lin, Drug != "CRISPR" & InG2P == "Yes")
test3 <- filter(cn_cor, Gene == "MET" & InG2P == "Yes")
```

## Specific plots

```{r, eval=FALSE}
ccle_prot$disease_g2p <- ifelse(ccle_prot$disease %in% g2p_diseases, ccle_prot$disease, "other")
ctrp_prot$disease_g2p <- ifelse(ctrp_prot$disease %in% g2p_diseases, ctrp_prot$disease, "other")
gdsc_prot$disease_g2p <- ifelse(gdsc_prot$disease %in% g2p_diseases, gdsc_prot$disease, "other")
ccle_signif_prot_summ <- filter(ccle_signif_prot, InG2P == "Yes") 
ctrp_signif_prot_summ <- filter(ctrp_signif_prot, InG2P == "Yes") 
gdsc_signif_prot_summ <- filter(gdsc_signif_prot, InG2P == "Yes") 
prot_drugs <- union(union(ccle_signif_prot_summ$Drug, ctrp_signif_prot_summ$Drug), gdsc_signif_prot_summ$Drug)
prot_drugs <- prot_drugs[!(prot_drugs %in% c("cabozantinib", "vandetanib"))]

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.04)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 3, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.02)
ht_prot_list <- ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))

png(filename = "./plots/prot_ht.png", width = 7, height = 6, units = "in", res = 500)
draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE)
dev.off()
```

```{r, eval=FALSE}
ccle_signif_g2p_dg_summ <- filter(ccle_signif_g2p_dg, InG2P == "Yes") 
ctrp_signif_g2p_dg_summ <- filter(ctrp_signif_g2p_dg, InG2P == "Yes") 
gdsc_signif_g2p_dg_summ <- filter(gdsc_signif_g2p_dg, InG2P == "Yes")

ccle_signif_g2p_dgl <- filter(ccle_signif_dgl, InG2P == "Yes") 
ctrp_signif_g2p_dgl <- filter(ctrp_signif_dgl, InG2P == "Yes") 
gdsc_signif_g2p_dgl <- filter(gdsc_signif_dgl, InG2P == "Yes")

signif_g2p_dg_summ <- rbind(ccle_signif_g2p_dg_summ, ctrp_signif_g2p_dg_summ, gdsc_signif_g2p_dg_summ)
signif_g2p_dg_summ <- unique(select(signif_g2p_dg_summ, Drug_Gene, p))
test <- filter(signif_g2p_dg_summ, p < 0.05)
length(unique(signif_g2p_dg_summ$Drug_Gene))

ccle_mut_filt <- filter(ccle, Drug_Gene == "crizotinib_ROS1")
ccle_mut_filt_plot <- ggplot(data = ccle_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  # facet_wrap(~ Drug_Gene, nrow = 1) +
  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
  geom_point(aes(color = as.character(Mutation)), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
  scale_color_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
  # scale_color_manual(values = g2p_disease_colors) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
  coord_cartesian(ylim = c(0, 1.10)) +
  # stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  annotate(geom = "text", label = "p = 0.0020", x = 1.5, y = 1.1) +
  labs(title = "CCLE: Crizotinib, ROS1", x = "Mutation Status", y = "AUC") +
  # guides(color = guide_legend(override.aes = list(size = 3))) +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
ggsave(plot = ccle_mut_filt_plot, filename = "./plots/crizotinib_ROS1_mut.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")

ccle_mut_filt <- filter(ccle, Drug_Gene == "erlotinib_EGFR")
ccle_mut_filt_plot <- ggplot(data = ccle_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  # facet_wrap(~ Drug_Gene, nrow = 1) +
  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
  scale_color_manual(values = g2p_disease_colors) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
  coord_cartesian(ylim = c(0, 1.10)) +
  # stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  annotate(geom = "text", label = "p = 0.0385", x = 1.5, y = 1.1) +
  labs(title = "CCLE: Erlotinib, EGFR", x = "Mutation Status", y = "AUC") +
  # guides(color = guide_legend(override.aes = list(size = 3))) +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
ggsave(plot = ccle_mut_filt_plot, filename = "./plots/erlotinib_EGFR_mut.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")

ctrp_mut_filt <- filter(ctrp, Drug_Gene == "vemurafenib_BRAF")
ctrp_mut_filt_plot <- ggplot(data = ctrp_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  # facet_wrap(~ Drug_Gene, ncol = 4) +
  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
  scale_color_manual(name = "Lineage", values = g2p_disease_colors) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
  coord_cartesian(ylim = c(0, 1.10)) +
  # stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  labs(title = "CTRP: Vemurafenib, BRAF", x = "Mutation Status", y = "AUC") +
  annotate(geom = "text", label = "p = 0.00045", x = 1.5, y = 1.1) +
  # guides(color = guide_legend(override.aes = list(size = 3))) +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
ggsave(plot = ctrp_mut_filt_plot, filename = "./plots/vemurafenib_BRAF_mut.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
